Presheaf Model for Dependent Types

### 2017-09-18 papers/talk-11/paper-11.tex
Connect CwF with the model
Mention support of pi and sigma types
Correct typo
Add rules for context morphisms

The next type former we consider is the $\Sigma$-type, or dependent sum,
corresponding to disjoint union in set theory. If we are given a family of sets
$(B_i)_{i \in I}$ we can form the set $\Sigma_{i \in I} B_i := \{ (i, b)~|~i
\in I \land b \in B_i\}$ whose elements consist of an index $i$ and an element
of the corresponding set $B_i$. In type theory the corresponding formation and
introduction rules look as follows.
\[
  \inference[$\Sigma$-F]{\Gamma \vdash A \text{ type}\\ \Gamma, x:A \vdash B \text{ type}}{\Gamma \vdash \Sigma x : A. B \text{ type}}
\]
\[
  \inference[$\Sigma$-I]{\Gamma \vdash a : A\\ \Gamma\vdash b: B[a / x]}{\Gamma Pair_{[x:A]B} (a,b) : \Sigma x : A. B}
\]

@@

@@

Let $\cat{C}$ be a small category. In the following objects of $\cat{C}$ will
be denoted as $I,J,K$ and morphisms as $f,g,h$.

>>>>

The next type former we consider is the $\Sigma$-type, or dependent sum,
corresponding to disjoint union in set theory. If we are given a family of sets
$(B_i)_{i \in I}$ we can form the set $\Sigma_{i \in I} B_i := \{ (i, b)~|~i
\in I \land b \in B_i\}$ whose elements consist of an index $i$ and an element
of the corresponding set $B_i$. In type theory the corresponding formation and
introduction rules look as follows.
\[
  \inference[$\Sigma$-F]{\Gamma \vdash A \text{ type}\\ \Gamma, x:A \vdash B \text{ type}}{\Gamma \vdash \Sigma x : A. B \text{ type}}
\]
\[
  \inference[$\Sigma$-I]{\Gamma \vdash a : A\\ \Gamma\vdash b: B[a / x]}{\Gamma \vdash Pair_{[x:A]B} (a,b) : \Sigma x : A. B}
\]

@@

We say that a category with families supports $\Pi$- and $\Sigma$-types if it's
closed under the corresponding rules shown in previous sections.

We also add the rules for context morphisms:

\[
  \inference{\Gamma \vdash A~type \qquad \sigma \from \Delta \to \Gamma}{\Delta \vdash A\sigma} \qquad
  \inference{\Gamma \vdash a : A \qquad \sigma \from \Delta \to \Gamma}{\Delta \vdash a\sigma : A\sigma}
\]
\[
  \inference{\sigma \from \Delta \to \Gamma \qquad \Gamma \vdash A \qquad \Delta \vdash a : A\sigma}{(\sigma, a) \from \Delta \to \Gamma.A}
\]

@@

We will now show how any presheaf category gives rise to a category with
families where the contexts are presheaves.  Let $\cat{C}$ be a small category.
In the following objects of $\cat{C}$ will be denoted as $I,J,K$ and morphisms
as $f,g,h$.
